\frb: Properties of VLA Bursts and Implications for Overall FRB Population

### 2016-11-18 repeater-vladata.tex
added figure and makefile

\title{\frb: Very Large Array Burst Properties and Implications for Overall FRB Population}
\shorttitle{\frb Burst Properties}
\shortauthors{Law et al.}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{}
\caption{Summary of observing coverage during VLA bursts.
\label{fig:multi}}
\end{center}
\end{figure}

@@

Observations during VLA bursts:
57643.420393  57643.478739 (PUPPI down; mock C band only)
57648.393437  57648.463303
57649.394722  57649.460378

@@

Observations during VLA bursts:
57643.3351  57643.4585
57645.3317  57645.4579
57648.3352  57648.4580
57649.3353  57649.4580

>>>>

\title{\frb: Properties of VLA Bursts and Implications for Overall FRB Population}
\shorttitle{\frb Burst Properties}
\shortauthors{Law et al.}

@@

\begin{figure*}[htb]
\begin{center}
\includegraphics[width=2\columnwidth]{timeline}
\caption{Summary of observing coverage during the multi-telescope observing campaign. Days with an observation are marked with symbols, while detections of \frb are enclosed in a black circle. The black dashed line shows the VLA burst detections with simultaneous coverage with other telescopes.
\label{fig:multi}}
\end{center}
\end{figure*}

@@

3 observations during VLA bursts...

@@

4 observations during VLA bursts...
